%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
% \begin{center}
%   {\LARGE \textbf{Peifeng Tan}}
% \end{center}

% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
% \textbf{\href{https://github.com/acse-pt623}{Peifeng Tan}} & University Email : \href{mailto:pt623@ic.ac.uk}{pt623@ic.ac.uk}\\
% \href{https://github.com/acse-pt623}{https://github.com/acse-pt623} & Personal Email : \href{mailto:tanxionji.1999@gmail.com}{tanxionji.1999@gmail.com} \\
% & Mobile : \href{tel:+4407826740870}{+44 07826740870} \\
% \end{tabular*}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\large Peifeng Tan} & \href{mailto:pt623@ic.ac.uk}{pt623@ic.ac.uk} \\
  \href{https://github.com/acse-pt623}{github.com/acse-pt623} & \href{mailto:tanxionji.1999@gmail.com}{tanxionji.1999@gmail.com} \\
  \href{tel:+4407826740870}{+44 07826740870} & \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Imperial College London}{London, UK}
    {Master of Applied Computational Science and Engineering}{Sep. 2023 -- Oct. 2024}
    \resumeItemListStart
      \resumeItem{Core Courses}
        {Machine Learning, Parallel Computing, Probability and Mathematical Statistics(100), Numerical methods, C++, Deep learning}
    \resumeItemListEnd

    \resumeSubheading
    {Chinese University of Petroleum-Beijing}{Beijing, China}
    {Bachelor of Engineering - Automation; GPA: 88.01/100}{Sep. 2017 -- June. 2021}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AIP}{London, UK}
      {Personal Research}{June 2024 - Present}
      \resumeItemListStart
        \resumeItem{Geonatiq LTD-Commodity Prices Prediction}
          {Use machine learning and sentiment analysis to predict commodity prices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Predicting Tropical Cyclone Behavior through Deep Learning}{}
      {Personal Research}{Jan 2024}
      \resumeItemListStart
      \item\small{
        {Constructed a deep learning model using PyTorch, predicting subsequent storm imagery for three future time points, and storm velocity for multiple consecutive moments, based on historical storm data and satellite imagery.}
      }
      \item\small{
        {Primarily responsible for building a CNN-ConvLSTM model, using the first ten time points of temporal labels, ocean labels, and storm images as input to predict the storm velocity at the last time point.}
      }
      \item\small{
        {GitHub: \href{https://github.com/ese-msc-2023/acds-the-day-after-tomorrow-yolanda.git}{https://github.com/ese-msc-2023/acds-the-day-after-tomorrow-yolanda.git}}
      }
      \resumeItemListEnd

      \resumeSubheading
      {Gerardium Rush Optimization Project}{}
      {Group Research}{May 2024}
      \resumeItemListStart
      \item\small{
        {Developed an optimization tool for mineral processing circuits using C++ and genetic algorithms. Enhanced computational efficiency with parallel processing via OpenMP and MPI.}
      }
      \item\small{
        {Key Achievements: Implemented core simulation and genetic algorithm in C++. Utilized OpenMP and MPI to accelerate simulations, improving performance and scalability.}
      }
      \item\small{
        {GitHub: \href{https://github.com/ese-msc-2023/acs-gerardium-rush-pentlandite}{https://github.com/ese-msc-2023/acs-gerardium-rush-pentlandite}}
      }
      \resumeItemListEnd

      \resumeSubheading
      {X-ray Finger Image Generation and Discrimination}{}
      {Personal Research}{Jan 2024}
      \resumeItemListStart
      \item\small{
        {In the first part, trained a GAN or VAE generative model to create images of human hands under X-ray.}
      }
      \item\small{
        {GitHub: \href{ https://github.com/ese-msc-2023/dlmodule-coursework-1-acse-pt623.git}{ https://github.com/ese-msc-2023/dlmodule-coursework-1-acse-pt623.git}}
      }
      \item\small{
        {In the second part, trained a ResNet34 model capable of distinguishing between real images, and those generated by GAN
        and VAE.}
      }
      \item\small{
        {GitHub: \href{ https://github.com/ese-msc-2023/dlmodule-coursework-2-acse-pt623.git}{ https://github.com/ese-msc-2023/dlmodule-coursework-2-acse-pt623.git}}
      }
      \resumeItemListEnd

      \resumeSubheading
      {Data Science and Big Data Analytics - Theory and Practice Online Project}{MIT}
      {Group Research,Professor Mark Vogelsberger, MIT}{Aug 2020 - Sep 2020}
      \resumeItemListStart
      \item\small{
        {Extracted data from the web and large databases, focusing on MongoDB. Developed machine learning models using TensorFlow and Keras.}
      }
      \item\small{
        {Implemented an AI-based doctor application capable of interacting with patients through NLP and detecting cancer through
        CNN-based image analysis.}
      }
      \item\small{
        {Implemented an AI-based doctor application for NLP and cancer detection using CNNs. Published a paper at IPEC 2021.}
      }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programme Languages}{: Python, C++, Matlab, Java, Assembly Language}
     \hfill
     \textbf{Language}{: Mandarin (native), English (fluent), French (beginner)}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
